---
title: "BIOSSCOPE_SDOM_master"
author: "Chance English"
date: "5/10/2023"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, echo = FALSE, warning = FALSE)

```


```{r}


library(tidyverse)
library(here)
library(ggplot2)
library(janitor)
library(ggsci)
library(lubridate)
library(readxl)
library(growthcurver)
library(zoo)
library(scales)
library(kableExtra)
library(broom)
library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(tidyverse)
library(reshape2)
library(vegan)
library(cowplot)

```



```{r}

BIOSSCOPE_sdom <- read_xlsx(here("data", "SDOM_DOC_CDOM_Summary.xlsx"), sheet = 1) %>% 
  mutate(zone = case_when(
    depth == "200m" ~ "Mesopelagic",
    depth == "1m" ~ "Surface",
    depth == "10m" ~ "Surface"
  ))



BIOSSCOPE_sdom_cdom <- read_xlsx(here("data", "SDOM_DOC_CDOM_Summary.xlsx"), sheet = 2)



```




# DOC Exudation Rates 

```{r}


SDOM_exudation <- read_xlsx(here("data", "SargDOM_exudate_summary_June_July_2021.xlsx"), sheet = 1)


SDOM_exud_exp <- SDOM_exudation %>% 
  filter(phase == "Exudation", experiment != "21_1") %>% 
  group_by(experiment, days, bottle,phys_state) %>% 
  summarise(doc_mgC = mean(DOC_uMC_gWW_d), sd_mgC = sd(DOC_uMC_gWW_d)) %>% 
  ungroup() %>% 
  mutate(hours = days*24) %>% 
  select(-days)


healthy_Sarg_DOM_production_rates <- SDOM_exud_exp %>% 
  group_by(experiment, bottle) %>% 
  nest() %>% 
  mutate(model = map(data, ~lm(doc_mgC ~ hours, data = .x) %>% 
                       tidy)) %>% 
  unnest(model) %>% 
  filter(term == "hours") %>% 
  select(experiment, bottle, estimate) %>% 
  mutate(mgC_g_hr = estimate) %>% 
  select(-estimate)
  
mean(healthy_Sarg_DOM_production_rates$mgC_g_hr)
sd(healthy_Sarg_DOM_production_rates$mgC_g_hr)


SDOM_21_2 <- SDOM_exud_exp %>% 
  filter(experiment == "21_2") 
SDOM_21_3 <- SDOM_exud_exp %>% 
  filter(experiment == "21_3") 



SDOM_sensescent_lm <- lm(doc_mgC ~ hours, data = SDOM_21_2)
SDOM_healthy_lm <- lm(doc_mgC ~ hours, data = SDOM_21_3)


summary(SDOM_sensescent_lm)
summary(SDOM_healthy_lm)


exud_plot <- SDOM_exud_exp %>% 
  ggplot(aes(x = hours/24, y = doc_mgC)) +
  geom_point(aes(color = phys_state), size = 10) +
  geom_errorbar(aes(color = phys_state, ymin = doc_mgC - sd_mgC, ymax = doc_mgC + sd_mgC)) +
  geom_smooth(method = "lm", aes(color = phys_state), se = FALSE) +
  scale_color_manual(values = c("darkgrey","black")) +
  labs(x = "Days") +
  ylab(expression(DOC~(µmolC ~ g[Sargassum]^{"-1"}))) +
  scale_x_continuous(limits = c(0,3.1), expand = c(0,0)) +
  scale_y_continuous(limits = c(0,500), expand = c(0,0.01)) +
  labs(color = c("Mature", "Senescent")) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = c(.18,.85),
        legend.text = element_text(size = 20),
        axis.text = element_text(size = 20, color = "black"),
        axis.title = element_text(size = 25),
        text = element_text(family = "Times"))




```




# ParV TOC 90 Days

```{r}

parv_plot <- BIOSSCOPE_sdom %>% 
  filter(parv_toc != "NA") %>% 
  mutate(zone = fct_relevel(zone, "Surface", "Mesopelagic")) %>% 
  ggplot(aes(x = days, y = parv_toc)) +
  geom_point(aes(color = exudate_condition), size = 5) +
  scale_color_manual(values = c("goldenrod2", "gray")) +
  geom_line(aes(color = exudate_condition))+ 
  labs(x = "Days",
       y = "% Initial DOC (µM)") +
  facet_grid(treatment~zone) +
  scale_x_continuous(limits = c(0,90)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black", size = 1.5),
        strip.text.x = element_text(),
        legend.key = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.text = element_text(size = 15),
        strip.text = element_text(size = "20"),
        axis.text = element_text(size = 15),
        axis.title = element_text(size = 17),
        text = element_text(family = "Times"),
        legend.position = "top")




```

# Summarize Ammendment Concnetration, Change over Entire Incubation and Percent Bioavailability

```{r}

# Calculate ammendments (µMC), the change in DOC relative to controls and the percent of the ammended DOC that remained after 80-90 days. Error for percent bioavailable is the standard error for the change in zeroed DOC divided by the DOC ammendment. 


bioavailability_sum_data <- BIOSSCOPE_sdom %>% 
 group_by(cruise, depth, exudate_condition) %>% 
  filter(parv_toc != "NA", period %in% c("T0", "TF")) %>% 
  summarize(treatment = c("Control", "SDOM", "SPE-SDOM"),
            ammendment_doc = round(parv_toc[timepoint == 0] - parv_toc[treatment == "Control" & timepoint == 0],1),
            se_ammendment_doc = round(sqrt(parv_toc_sd[timepoint == 0]^2 + parv_toc_sd[treatment == "Control" & timepoint == 0]^2),1),
            delta_doc_90 = round((parv_toc[period == "TF"] - parv_toc[period == "T0"])*-1,1),
            se_delta_doc_90 = round(sqrt(parv_toc_sd[timepoint==0]^2 + parv_toc_sd[treatment == "Control" & timepoint == 0]^2),1),
            delta_doc_90_zeroed = round((delta_doc_90 - delta_doc_90[treatment == "Control"]),1),
            se_delta_doc_90_zeroed = round(sqrt(se_delta_doc_90^2 + se_delta_doc_90[treatment == "Control"]^2),1),
            percent_bioavailable = round((delta_doc_90_zeroed / ammendment_doc)*100,0),
            se_percent_bioavailable = round((se_delta_doc_90_zeroed/ammendment_doc)*100,0)) %>% 
  ungroup() %>% 
  mutate(incubation_zone = case_when(
    depth %in% c("1m", "10m") ~ "Surface",
    depth == "200m" ~ "Mesopelagic"
  )) %>% 
  filter(treatment != "Control") %>% 
  mutate(treatment_phys = paste(exudate_condition, treatment, sep = " "))


# Plot showing the percent of amended DOC which remained after 80-90 days +/- the error in this percentage. 

recalcitrance_plot <- bioavailability_sum_data %>%
  ggplot(aes(x = reorder(treatment_phys, -percent_bioavailable), y = percent_bioavailable, fill = incubation_zone)) +
  geom_bar(stat = "identity", position = position_dodge(), clor = "black") +
  geom_errorbar(aes(ymin = percent_bioavailable - se_percent_bioavailable, ymax = percent_bioavailable + se_percent_bioavailable), width = 0, position = position_dodge(0.8)) +
  labs(y = "Bioavailable DOC (% Amended)",
       x = "") +
  scale_fill_manual(values = c("indianred","steelblue3")) +
  scale_x_discrete(labels = c("Sensescent \n+DOC", "Mature \n+DOC", "Sensecent \n+SPE-DOC", "Mature \n+SPE-DOC")) + scale_y_continuous(breaks = c(0,25,50,75,100)) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        plot.margin = margin(0.5,0.5,0.5,0.5, "cm"),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = c(.8,.88),
        legend.text = element_text(size = 25),
        axis.text.x = element_text(size = 20, vjust = 0.5, color = "black"),
        axis.text.y = element_text(size = 20, color = "black"),
        axis.title = element_text(size = 25),
        text = element_text(family = "Times")) 


recalcitrance_plot <- bioavailability_sum_data %>%
  ggplot(aes(x = reorder(treatment_phys, -percent_bioavailable), y = percent_bioavailable, fill = incubation_zone)) +
  geom_bar(stat = "identity", position = position_dodge(), clor = "black") +
  geom_errorbar(aes(ymin = percent_bioavailable - se_percent_bioavailable, ymax = percent_bioavailable + se_percent_bioavailable), width = 0, position = position_dodge(0.8)) +
  labs(y = "% Bioavailable",
       x = "") +
  scale_fill_manual(values = c("indianred","steelblue3")) +
  scale_x_discrete(labels = c("Sensescent \n Whole", "Mature \n Whole", "Sensecent \n SPE", "Mature \n SPE")) + scale_y_continuous(breaks = c(0,25,50,75,100)) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        plot.margin = margin(0.5,0.5,0.5,0.5, "cm"),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = c(.8,.88),
        legend.text = element_text(size = 25),
        axis.text.x = element_text(size = 20, vjust = 0.5, color = "black"),
        axis.text.y = element_text(size = 20, color = "black"),
        axis.title = element_text(size = 25),
        text = element_text(family = "Times")) 





```


# Treatments & Bioavailability Summary Data Table

```{r}

# Load phenolic content data

phenolic_content <- read_xlsx(here("data", "Sargassum_recalcitrance.xlsx"))

  
phenolic_content_clean <- phenolic_content %>% 
  select(exudate_condition, incubation_zone, treatment, TPC_HMW_percentDOC, sd_TPC_percent_DOC, Ammendment, ) %>% 
  mutate(TPC_HMW_percentDOC = round(TPC_HMW_percentDOC,1),
         sd_TPC_percent_DOC = round(sd_TPC_percent_DOC,1))


bioavailability_sum_data_clean <- bioavailability_sum_data %>% 
  mutate(exudate_condition = case_when(
    exudate_condition == "Senescent" ~ "Senescent",
    exudate_condition == "Mature" ~ "Healthy"
  )) %>% 
  select(exudate_condition, treatment, ammendment_doc, se_ammendment_doc, percent_bioavailable, se_percent_bioavailable, incubation_zone)
  

bioavailability_sum_phenolic <- merge(phenolic_content_clean, bioavailability_sum_data_clean, 
                                      by = c("exudate_condition", "incubation_zone", "treatment"))


bioavailability_sum_phenolic$amended_DOC_se <- paste(bioavailability_sum_phenolic$ammendment_doc,
                                                bioavailability_sum_phenolic$se_ammendment_doc,
                                                     sep = "±")

bioavailability_sum_phenolic$bioavailable_DOC_se = paste(bioavailability_sum_phenolic$percent_bioavailable,                                                     bioavailability_sum_phenolic$se_percent_bioavailable, 
                                                         sep = "±")

bioavailability_sum_phenolic$phenolic_se = paste(bioavailability_sum_phenolic$TPC_HMW_percentDOC, 
                                                 bioavailability_sum_phenolic$sd_TPC_percent_DOC, sep = "±") 



bioavailability_sum_phenolic_clean <- bioavailability_sum_phenolic %>% 
  select(exudate_condition, incubation_zone, Ammendment, amended_DOC_se, phenolic_se, bioavailable_DOC_se)


amendment_bioavailability_table <- kbl(bioavailability_sum_phenolic_clean,
                                       booktabs = TRUE,
                                       col.names = c("Physiological State", 
                                                     "Depth Zone", 
                                                     "Treatment","DOC Amended (µMC)", 
                                                     "TPC (%DOC)", 
                                                     "Bioavailability (%)")) %>% 
  kable_classic(html_font = "Times New Roman",
                  full_width = F) %>% 
  kable_styling(font_size = 20)


```


#a275nm over time plot 

```{r}

AE2213_CDOM_long <- melt(BIOSSCOPE_sdom_cdom, id = 'wvln_2', variable.name = 'CDOM_code')

BIOSSCOPE_sdom_cdom_metadata <- BIOSSCOPE_sdom %>% 
  select(cruise, days, depth, exudate_condition, period,treatment, CDOM_code)


BIOSSCOPE_cdom_metadata <- merge(AE2213_CDOM_long, BIOSSCOPE_sdom_cdom_metadata, by = "CDOM_code")

BIOSSCOPE_cdom_metadata_270 <- BIOSSCOPE_cdom_metadata %>% 
  filter(wvln_2 == 275)


a275nm_cdom_time_plot <- BIOSSCOPE_cdom_metadata_270 %>% 
   mutate(depth_zone =
           case_when(depth %in% c("1m", "10m") ~ "Surface",
                     depth == "200m" ~ "Mesopelagic")) %>% 
  ggplot(aes(x = days, y = value, color = treatment)) +
  geom_point(size = 5) +
  geom_line(size = 1) +
  labs(x = "Days") +
  ylab(expression(a["275nm"]~(m^{"-1"}))) +
  facet_grid(.~factor(depth_zone, levels = c("Surface", "Mesopelagic"))) +
  scale_y_continuous(limits = c(0,2)) +
  scale_color_manual(values = c("blue", "brown2", "goldenrod1"), labels = c("Control", "+DOC", "+SPE-DOC")) + 
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        plot.margin = margin(0.5,0.5,0.5,0.5, "cm"),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = "top",
        legend.text = element_text(size = 20),
        axis.text.x = element_text(size = 20, vjust = 0.5, color = "black"),
        axis.text.y = element_text(size = 20, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times"),
        panel.spacing = unit(3, "lines"),
        strip.text.x = element_text(size = 20)) 


```


# Absorption 275nm Remaining after 3 months 


```{r}

BIOSSCOPE_cdom_metadata_270 %>% 
  filter(period != "NA") %>% 
  filter(depth == "200m") %>% 
  group_by(treatment) %>% 
  summarize(percent_275nm = (value[period == "TF"]/value[period == "T0"])*100) %>% 
  filter(percent_275nm != "NA")

BIOSSCOPE_cdom_metadata_270 %>% 
  filter(period != "NA") %>% 
  filter(depth == "1m") %>% 
  group_by(treatment) %>% 
  summarize(percent_275nm = (value[period == "TF"]/value[period == "T0"])*100) %>% 
  filter(percent_275nm != "NA") 




```

# CDOM T0 TFinal Plots for Mature Incubations

```{r}

CDOM_T0_TF_plots <- BIOSSCOPE_cdom_metadata %>% 
  mutate(depth_zone =
           case_when(depth %in% c("1m", "10m") ~ "Surface",
                     depth == "200m" ~ "Mesopelagic")) %>% 
  filter(period %in% c("T0", "TF")) %>% 
  ggplot(aes(x = wvln_2, y = value, color = treatment, linetype = period)) +
  geom_line(size = 2) +
  labs(x = "Wavelength (nm)") +
  ylab(expression(a~(m^{"-1"}))) +
  facet_grid(.~factor(depth_zone, levels = c("Surface", "Mesopelagic"))) +
  scale_x_continuous(limits = c(250,600)) +
  scale_y_continuous(limits = c(0,2), breaks = c(0.5,1,1.5,2)) +
  scale_color_manual(values = c("blue", "brown2", "goldenrod1")) + 
  scale_linetype_manual(values = c("solid", "longdash")) +
  coord_cartesian(expand = c(0,0)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        plot.margin = margin(0.5,0.5,0.5,0.5, "cm"),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = c(0.8,0.8),
        legend.text = element_text(size = 15),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black", hjust = 0.5),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times"),
        panel.spacing = unit(3, "lines"),
        legend.key.width = unit(2.5, "cm"),
        strip.text.x = element_text(size = 20)) +
  guides(color = F)









```



# Figure 2

```{r}



figure2 <- plot_grid(a275nm_cdom_time_plot, CDOM_T0_TF_plots, nrow = 2, labels = c('A', 'B'), label_fontfamily = "Times New Roman", label_size = 20)




```





#CDOM Ammended T0 (Specific Absorption Ammended)

```{r}

CDOM_T0_ammended <- BIOSSCOPE_sdom_cdom <- read_xlsx(here("data", "SDOM_DOC_CDOM_Summary.xlsx"), sheet = 3)

CDOM_T0_ammended_long <- melt(CDOM_T0_ammended, id = 'wvln_2', variable.name = 'CDOM_T0')

BIOSSCOPE_sdom_cdom_metadata_CDOM_T0 <- BIOSSCOPE_sdom %>% 
  select(cruise, days, depth, exudate_condition, period,treatment, CDOM_T0)


BIOSSCOPE_cdom_T0_metadata <- merge(CDOM_T0_ammended_long, BIOSSCOPE_sdom_cdom_metadata_CDOM_T0, by = "CDOM_T0")

BIOSSCOPE_cdom_T0_metadata_blanked <- BIOSSCOPE_cdom_T0_metadata %>% 
  group_by(cruise, exudate_condition, wvln_2,depth) %>% 
  mutate(blanked_abs = value - value[treatment == "Control"]) %>% 
  ungroup() %>% 
  select(cruise, depth,exudate_condition, treatment, wvln_2 ,blanked_abs) 


specific_ag_amended_plot <- BIOSSCOPE_cdom_T0_metadata_blanked %>% 
  filter(treatment != "Control") %>% 
  group_by(depth, exudate_condition, treatment) %>% 
  ggplot(aes(x = wvln_2, y = blanked_abs, linetype = exudate_condition, shape = depth)) +
  geom_line(aes(color = treatment), size = 1, orientation = "x") +
  scale_x_continuous(limits = c(250, 600)) + 
  scale_y_continuous(limits = c(0, 0.02), breaks = c(0, 0.01,0.02)) +
  scale_color_manual(values = c("brown2", "goldenrod1"), labels = c("+DOC", "+SPE-DOC")) +
  ylab(expression(Amended~Specific~a~(m^{"-1"}~µMC^{-1}))) +
  geom_rect(aes(xmin = 265, xmax = 285, ymin = -Inf, ymax = Inf), fill = "cyan", alpha = 0.003) +
  geom_vline(aes(xintercept = 275), size = 2, linetype = 1, alpha = 1) +
  labs(x = "Wavelength (nm)") +
  coord_cartesian(expand = c(0,0)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        plot.margin = margin(0.5,0.5,0.5,0.5, "cm"),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white", color = "white"),
        legend.title = element_blank(),
        legend.position = c(0.7,0.8),
        legend.text = element_text(size = 20),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black", hjust = 0.5),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times"),
        panel.spacing = unit(3, "lines"),
        legend.key.width = unit(2, "cm"),
        strip.text.x = element_text(size = 20)) 






```

# Merge Specific 275 abosorption with bioavailability summary data 


```{r}

# Filter specific ammended data for only absorption at 275 nm


BIOSSCOPE_cdom_T0_metadata_blanked_270 <- BIOSSCOPE_cdom_T0_metadata_blanked %>% 
  filter(wvln_2 == 275) %>% 
  filter(treatment != "Control")

# Rename treatments to match for merging

bioavailability_sum_data_rename <- bioavailability_sum_data %>% 
  mutate(treatment = case_when(
    treatment == "SPE-SDOM" ~ "SDOM PPL",
    treatment == "SDOM" ~ "SDOM"
  ))


# Merge two dataframes

ammended270_recalcitrantDOC <- merge(bioavailability_sum_data_rename, BIOSSCOPE_cdom_T0_metadata_blanked_270, by = c("exudate_condition", "treatment","depth"))

# Model 1 and 2 Regression for % Bioavailable and Ammended Specific Absorption at 275

percent_bioavailable_model1 <- lm(percent_bioavailable~blanked_abs, data = ammended270_recalcitrantDOC)
  
percent_bioavailable_model2 <- lmodel2::lmodel2(percent_bioavailable~blanked_abs, data = ammended270_recalcitrantDOC)


# Plot Regression of Ammended 275 nm and Percent Bioavailable 

ammended_275_plot <- ammended270_recalcitrantDOC %>% 
  ggplot(aes(x = blanked_abs, y = percent_bioavailable)) +
  geom_point(size = 6) +
  geom_abline(intercept = 99.79, slope = -5032.85,size = 1) +
  xlab(expression(Amended~Specific~a["275nm"]~(m^{"-1"}~µMC^{-1}))) +
  labs(y = "Bioavailable DOC (% Amended)") + 
  scale_y_continuous(limits = c(0,105, breaks = c(25,50,75,100))) +
  scale_x_continuous(limits = c(0.000, 0.017), breaks = c(0.005,0.010,0.015)) +
   coord_cartesian(expand = c(0,0)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = c(0.85,0.7),
        legend.text = element_text(size = 15),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black", hjust = 0.5),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times")) 
  






```


# Figure 1

```{r}

figure1 <- plot_grid(specific_ag_amended_plot, ammended_275_plot,labels = c('A', 'B'), label_size = 20, label_fontfamily = "Times New Roman")





```



# Linear Regression between Phenolic Content and SUVA_275n



```{r}


a270_specific_amended_short <- ammended270_recalcitrantDOC %>% 
  select(exudate_condition, depth, treatment, incubation_zone, blanked_abs) %>% 
  mutate(treatment = case_when(
    treatment == "SDOM" ~ "SDOM",
    treatment == "SDOM PPL" ~ "SPE-SDOM"
  ),
  exudate_condition = case_when(
    exudate_condition == "Mature" ~ "Healthy",
    exudate_condition == "Senescent" ~ "Senescent"
  ))

phenol_recalcitrance_short <- phenolic_content_clean %>% 
  select(TPC_HMW_percentDOC, incubation_zone, treatment, exudate_condition)


a270_specific_amended_TPC <- merge(a270_specific_amended_short, phenol_recalcitrance_short, by = c("incubation_zone", "treatment", "exudate_condition"))




lm_a270_TPC <- lm(blanked_abs ~ TPC_HMW_percentDOC, data = a270_specific_amended_TPC)

summary(lm_a270_TPC)

a270_TPC_p <- a270_specific_amended_TPC %>% 
  ggplot(aes(x = TPC_HMW_percentDOC , y = blanked_abs)) +
  geom_point(size = 6) +
  geom_abline(intercept = 0.0026, slope = 0.000292, size = 1) +
  ylab(expression(Amended~Specific~a["275nm"]~(m^{"-1"}~µMC^{-1}))) +
  labs(x = "Exudate TPC (%DOC)") + 
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = c(0.85,0.7),
        legend.text = element_text(size = 15),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black", hjust = 0.5),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times")) 

```


# Phenol Percent of Recalcintrant DOC


```{r}
bioavailability_sum_phenolic %>% 
  select(TPC_HMW_percentDOC, percent_bioavailable) %>% 
  mutate(percent_recalcitrant = 100 - percent_bioavailable) %>% 
  mutate(percent_phenol_recalcitrant = (TPC_HMW_percentDOC/percent_recalcitrant)*100) %>% 
  mutate(percent_phenol_recalcitrant = case_when(
    percent_phenol_recalcitrant
  ))
  select(percent_phenol_recalcitrant)
```


# Two-sample t-test for Specific a275 amendment by treatment

```{r}

# Specific a275nm amendment by treatment 

with(ammended270_recalcitrantDOC, shapiro.test(blanked_abs[treatment == "SDOM"])) # p = 0.487
with(ammended270_recalcitrantDOC, shapiro.test(blanked_abs[treatment == "SDOM PPL"])) # p = 0.7448

sa275nm_f.test <- var.test(blanked_abs ~ treatment, data = ammended270_recalcitrantDOC)
sa275nm_f.test # p-value = 0.6716 so variances are equal 



a275nm_treatment_t.test <- t.test(blanked_abs ~ treatment, data = ammended270_recalcitrantDOC, var.equal = TRUE)

a275nm_treatment_t.test


```


# Two-sample t-test for Percent Bioavailability vs treatment 

```{r}

# Specific a275nm amendment by treatment 

with(ammended270_recalcitrantDOC, shapiro.test(percent_bioavailable[treatment == "SDOM"])) # p = 0.7275
with(ammended270_recalcitrantDOC, shapiro.test(percent_bioavailable[treatment == "SDOM PPL"])) # p = 0.7257

percent_bioavailable_f.test <- var.test(percent_bioavailable ~ treatment, data = ammended270_recalcitrantDOC)
percent_bioavailable_f.test # p-value = 0.7543 so variances are equal 



percent_bioavailble_t.test <- t.test(percent_bioavailable ~ treatment, data = ammended270_recalcitrantDOC, var.equal = TRUE, alternative = "greater")

percent_bioavailble_t.test


```

# Two-sample t-test for Percent Bioavailability vs depth 

```{r}

# Specific a275nm amendment by treatment 

with(ammended270_recalcitrantDOC, shapiro.test(percent_bioavailable[incubation_zone == "Surface"])) # p = 0.7011
with(ammended270_recalcitrantDOC, shapiro.test(percent_bioavailable[incubation_zone == "Mesopelagic"])) # p = 0.8548

percent_bioavailable_depth_f.test <- var.test(percent_bioavailable ~ incubation_zone, data = ammended270_recalcitrantDOC)

percent_bioavailable_depth_f.test # p-value = 0.7543 so variances are equal 



percent_bioavailble_t.test <- t.test(percent_bioavailable ~ treatment, data = ammended270_recalcitrantDOC, var.equal = TRUE, alternative = "greater")

percent_bioavailble_t.test


```



# Photooxidation Experiments 

```{r}

SDOM_PD_exp <- read_xlsx(here("data", "SDOM_DOC_CDOM_Summary.xlsx"), sheet = 4)

SDOM_PD_cdom <- read_xlsx(here("data", "SDOM_DOC_CDOM_Summary.xlsx"), sheet = 5)




```

#Delta DIC, DOC


```{r}

# DIC

PD_DIC <- SDOM_PD_exp %>% 
  ggplot(aes(x = time_hr, y = DIC_uM, color = treatment)) +
  geom_point(size = 8) +
  geom_line(size = 1) +
  geom_errorbar(aes(ymin = DIC_uM - DIC_sd, ymax = DIC_uM + DIC_sd), width = 0) +
  scale_color_manual(values = c("black", "goldenrod2")) +
  scale_y_continuous(limits = c(-2,32), breaks = c(0,10,20,30)) +
  labs(y = "∆DIC (µMC)",
       x = "Hours") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_blank(),
        legend.title = element_blank(),
        legend.position = "none",
        legend.text = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black", hjust = 0.5),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times")) 
  
#DOC

PD_DOC <- SDOM_PD_exp %>% 
  ggplot(aes(x = time_hr, y = DOC_uMC, color = treatment)) +
  geom_point(size = 8) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(-35,2), breaks = c(0,-10,-20,-30)) +
  geom_errorbar(aes(ymin = DOC_uMC - DOC_sd, ymax = DOC_uMC + DOC_sd), width = 0) +
  scale_color_manual(values = c("black", "goldenrod2")) +
  labs(y = "∆DOC (µMC)",
       x = "Hours") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = c(0.2,0.2),
        legend.text = element_text(size = 15),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black", hjust = 0.5),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times")) 

# DOC vs DIC


SDOM_PD_exp %>% 
  filter(treatment != "Dark") %>% 
  ggplot(aes(x = -DOC_uMC, y = DIC_uM)) +
  geom_point(size = 1) +
  geom_smooth(method = "lm") +
  geom_errorbar(aes(ymin = DIC_uM - DIC_sd, 
                    ymax = DIC_uM + DIC_sd), 
                width = 0) +
  geom_errorbar(aes(xmin = -DOC_uMC - DOC_sd, 
                    xmax = -DOC_uMC + DOC_sd), 
                width = 0) +
  scale_y_continuous(limits = c(-2,0,35), breaks = c(0,10,20,30)) +
  geom_abline(slope = 1, intercept = 0, color = "black") +
  scale_color_manual(values = c("black", "goldenrod2")) +
  labs(y = "∆DIC (µMC)",
       x = "∆DOC (µMC)") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = c(0.15,0.15),
        legend.text = element_text(size = 15),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black", hjust = 0.5),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times")) 



# PGE 

PD_PGE <- SDOM_PD_exp %>% 
  ggplot(aes(x = time_hr, y = PGE_uMC, color = treatment)) +
  geom_point(size = 8) +
  geom_line(size = 1) +
  geom_errorbar(aes(ymin = PGE_uMC - PGE_sd, ymax = PGE_uMC + PGE_sd), width = 0) +
  scale_color_manual(values = c("black", "goldenrod2")) +
  labs(y = "TPC (µMC-PGE)",
       x = "Hours") +
  scale_y_continuous(limits = c(-2,35), breaks = c(0,10,20,30)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.title = element_blank(),
        legend.position = "none",
        legend.text = element_blank(),
        axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black", hjust = 0.5),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times")) 


#CDOM

SDOM_PD_cdom_long <- melt(SDOM_PD_cdom, id = "wvln_2", variable.name = "CDOM_code")


SDOM_PD_exp_metadata <- SDOM_PD_exp %>% 
  select(experiment, time_hr, treatment,CDOM_code)


SDOM_PD_cdom_metadata <- merge(SDOM_PD_cdom_long, SDOM_PD_exp_metadata, by = "CDOM_code")

PD_CDOM <- SDOM_PD_cdom_metadata %>% 
  mutate(time_hr = as.factor(time_hr)) %>% 
  ggplot(aes(x = wvln_2, y = value, color = treatment, shape = experiment)) +
  geom_line(aes(linetype = time_hr), size = 2, position = position_jitter(h = 0.01 ,w = 0)) +
  labs(x = "Wavelength (nm)") +
  scale_linetype_manual(values = c("solid","dashed","dotted")) +
  ylab(expression(a~(m^{"-1"}))) +
  labs(linetype = "Time (hr)") +
  scale_y_continuous(limits = c(0,20)) +
  scale_x_continuous(limits = c(250,600)) +
  coord_cartesian(expand = c(0,0)) +
  scale_color_manual(values = c("black", "goldenrod2")) + 
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        plot.margin = margin(0.5,0.5,0.5,0.5, "cm"),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.title = element_text(size = 15, hjust = 0.5),
        legend.position = c(0.7,0.7),
        legend.text = element_text(size = 15),
        legend.key.width = unit(3, "cm"),
        axis.text.x = element_text(size = 20, vjust = 0.5, color = "black"),
        axis.text.y = element_text(size = 20, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times"),
        panel.spacing = unit(3, "lines"),
        strip.text.x = element_text(size = 20)) +
  guides(color = "none")
  


figure3 <- plot_grid(PD_DOC, PD_PGE, PD_DIC, PD_CDOM, labels = c('A', 'B','C','D'), label_size = 20, label_fontfamily = "Times New Roman")

```

